Predictive Regressions with Persistent Regressors

### 2019-09-09 paper.tex
ADD garch estimation

\begin{aligned} \epsilon_{t} &=h_{t} \eta_{t}, \quad \eta_{t} \stackrel{i i d}{\sim}(0,1) \\ h_{t}^{2} &=\omega+\sum_{i=1}^{q} \alpha_{i} \epsilon_{t-i}^{2}+\sum_{i=1}^{p} \beta_{i} h_{t-i}^{2} \\ \omega &>0, \quad \alpha_{i} \geq 0, \quad i=1, \ldots, q, \quad \beta_{i} \geq 0, \quad i=1, \ldots, p \end{aligned}

@@

In the CCC-GARCH model it has been assumed that there are no volatility transmissions between the returns and the regressor. This assumption seems unrealistic and it reduces the correlation between the residuals as demonstrated by $\hat{\delta}$. There are various multivariate GARCH models suited for incorporating spill-over effects such as the BEKK model of Engle and Kroner (1995). It seems plausible, though, that the variances of both the regressor and the returns share a common stochastic trend which may be imagined as the overall economic uncertainty. This seems reasonable since it is hard to imagine having high variance in returns without having high variance in valuation ratios and vice versa. Simulation is performed similar as in the CCC-GARCH model but now $h_{1, t} =h_{2, t}$ in equation ($\ref{eqn:40}$). Results in Table~\vref{tab:cst-garch} compared with Table~\vref{tab:cy}  indicate that the one-sided Bonferroni Q-test tends to over-reject the true null if innovations are modeled as described above.
\begin{table}[hbt]
\centering
\caption{Finite-sample rejection rates (common stochastic trend)}
\label{tab:cst-garch}
\begin{threeparttable}
\begin{tabular}{rrrrrrrrrr}
  \hline
  & Obs & $c$ & $\rho$ & $\delta$ & $\alpha_{_{GARCH}}$ & $\beta_{_{GARCH}}$ & t-test &BQ& BQ$_{{2sided}}$ \\ 
  \hline
1 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.90 & 0.2815 & 0.0952 & 0.0990 \\ 
  2 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.80 & 0.2762 & 0.1009 & 0.1048 \\ 
  3 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.50 & 0.2706 & 0.0942 & 0.0977 \\ 
  4 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.40 & 0.2676 & 0.0961 & 0.1004 \\ 
  5 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.30 & 0.2628 & 0.0932 & 0.0972 \\ 
  6 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.20 & 0.2704 & 0.0908 & 0.0943 \\ 
  7 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.10 & 0.2677 & 0.0935 & 0.0984 \\ 
  8 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.90 & 0.3135 & 0.0733 & 0.0771 \\ 
  9 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.80 & 0.2812 & 0.0703 & 0.0771 \\ 
  10 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.50 & 0.2780 & 0.0683 & 0.0747 \\ 
  11 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.40 & 0.2797 & 0.0676 & 0.0742 \\ 
  12 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.30 & 0.2758 & 0.0664 & 0.0734 \\ 
  13 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.20 & 0.2746 & 0.0629 & 0.0703 \\ 
  14 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.10 & 0.2749 & 0.0656 & 0.0715 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed [BQ] and two-tailed  [BQ$_{{2sided}}$] Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with the variances of innovations sharing a common stochastic trend which is modeled as a univariate GARCH(1, 1) process. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\bibitem{} 
{Campbell, J. Y., Yogo, M. }
\textit{Efficient tests of stock return predictability.} Journal of Financial Economics 81, 27-60, 2006.
\bibitem{} 
{Elliott, G., Stock, J.H.} \textit{Inference in time series regression when the order of integration of a regressor is
unknown.} Econometric Theory 10, 672–700,  1994.
\bibitem{} 
Elliott, G., Rothenberg, T. J., \& Stock, J. H. (1996). Efficient Tests for an Autoregressive Unit Root. Econometrica, 64(4), 813–836.
\bibitem{} 
Jacquier, E., Polson, N.G., Rossi, P.E., 2004. Bayesian analysis of stochastic volatility
models with fat-tails and correlated errors. J. Econometrics 122, 185–212.
\bibitem{} 
Cavaliere, G., 2004. Unit root tests under time-varying variances. Econometric Rev.
23, 259–292.
\bibitem{} 
Phillips, P. C. B., 2014, On confdence Intervals for autoregressive roots and predictive regression. Econometrica, 82(3), 1177-1195.
\bibitem{} 
Bollerslev (1990): Modelling the coherence in short–run nominal exchange rates: a multivariate generalized ARCH model, Review of Economics and Statistics, 73, 498–505.
\bibitem{} 
Engle and Kroner (1995). Multivariate Simultaneous Generalized ARCH, Econometric Theory, 11, 122–150.
\end{thebibliography}

>>>>

\label{eqn:garch}
\begin{aligned} \epsilon_{t} &=h_{t} \eta_{t}, \quad \eta_{t} \stackrel{i i d}{\sim}N(0,1) \\ h_{t}^{2} &=\omega+\sum_{i=1}^{q} \alpha_{i} \epsilon_{t-i}^{2}+\sum_{i=1}^{p} \beta_{i} h_{t-i}^{2} \\ \omega &>0, \quad \alpha_{i} \geq 0, \quad i=1, \ldots, q, \quad \beta_{i} \geq 0, \quad i=1, \ldots, p \end{aligned}

@@

In the CCC-GARCH model it has been assumed that there are no volatility transmissions between the returns and the regressor. This assumption seems unrealistic and it reduces the correlation between the residuals as demonstrated by $\hat{\delta}$. There are various multivariate GARCH models suited for incorporating spill-over effects such as the BEKK model of Engle and Kroner (1995). It seems plausible, though, that the variances of both the regressor and the returns share a common stochastic trend which may be imagined as the overall economic uncertainty. This seems reasonable since it is hard to imagine having high variance in returns without having high variance in valuation ratios and vice versa. Parameter estimates of the univariate GARCH model based on monthly returns from 1926 to 2003 are displayed in Table~\vref{tab:garch_est}. Since $\hat{\alpha}+\hat{\beta}=0.983$ is close to 1, at which point the covariance stationarity condition is violated, concern of conditional heteroskedasticity of real returns leading to invalid inference using the feasible Q-test is justified.
\begin{table}[!htbp] \centering 
  \caption{Parameter Estimates of the GARCH(1, 1)} 
  \label{tab:garch_est} 
  \begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 &  Estimate &  Rob. Std. Error &  Rob. t value & Pr(\textgreater \textbar t\textbar ) \\ 
\hline \\[-1.8ex] 
$\omega$ & $0.0001$ & $0.00002$ & $2.553$ & $0.011$ \\ 
$\alpha$ & $0.107$ & $0.020$ & $5.331$ & $0.000$ \\ 
$\beta$ & $0.876$ & $0.020$ & $44.365$ & $0.000$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
 \begin{tablenotes}
 \small
\item Data is taken from Motohiro Yogo's website. Returns are the CRSP value weighted index log-returns from 1926 to 2003 minus the risk free rate.
\end{tablenotes}
\end{threeparttable}
\end{table}

Simulation is performed similar as in the CCC-GARCH model but now $h_{1, t} =h_{2, t}$ in equation ($\ref{eqn:40}$). Results in Table~\vref{tab:cst-garch} compared with Table~\vref{tab:cy}  indicate that the one-sided Bonferroni Q-test tends to over-reject the true null if innovations are modeled as described above.
\begin{table}[hbt]
\centering
\caption{Finite-sample rejection rates (common stochastic trend)}
\label{tab:cst-garch}
\begin{threeparttable}
\begin{tabular}{rrrrrrrrrr}
  \hline
  & Obs & $c$ & $\rho$ & $\delta$ & $\alpha_{_{GARCH}}$ & $\beta_{_{GARCH}}$ & t-test &BQ& BQ$_{{2sided}}$ \\ 
  \hline
1 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.90 & 0.2815 & 0.0952 & 0.0990 \\ 
  2 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.80 & 0.2762 & 0.1009 & 0.1048 \\ 
  3 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.50 & 0.2706 & 0.0942 & 0.0977 \\ 
  4 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.40 & 0.2676 & 0.0961 & 0.1004 \\ 
  5 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.30 & 0.2628 & 0.0932 & 0.0972 \\ 
  6 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.20 & 0.2704 & 0.0908 & 0.0943 \\ 
  7 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.10 & 0.2677 & 0.0935 & 0.0984 \\ 
  8 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.90 & 0.3135 & 0.0733 & 0.0771 \\ 
  9 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.80 & 0.2812 & 0.0703 & 0.0771 \\ 
  10 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.50 & 0.2780 & 0.0683 & 0.0747 \\ 
  11 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.40 & 0.2797 & 0.0676 & 0.0742 \\ 
  12 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.30 & 0.2758 & 0.0664 & 0.0734 \\ 
  13 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.20 & 0.2746 & 0.0629 & 0.0703 \\ 
  14 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.10 & 0.2749 & 0.0656 & 0.0715 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed [BQ] and two-tailed  [BQ$_{{2sided}}$] Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with the variances of innovations sharing a common stochastic trend which is modeled as a univariate GARCH(1, 1) process. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}

Glosten, Jagannathan and Runkle (1993) [GJR] observe that in financial markets negative shocks contribute disproportionately more to future return volatility than positive shocks. To model the dynamics of real markets more adequately, innovation variances are modeled by a common univariate GJR-GARCH process. This process models conditional variance as
\begin{equation}
h_{t}^{2}=\omega+\left(\alpha+\gamma S_{t-1}\right) \epsilon_{t-1}^{2}+\beta h_{t-1}^{2}
\end{equation}
where $$S_{t-1}=\left\{\begin{array}{ll}{1} & {\text { if } \epsilon_{t-1}<0} \\ {0} & {\text { if } \epsilon_{t-1} \geq 0}\end{array}\right..$$
When $\gamma>0$ negative shocks increase volatility more than positive shocks. The GJR-GARCH process is covariance stationary if $\alpha+\gamma / 2+\beta<1$. Further, to allow for conditional leptokurtosis $\eta_{t}$ in equation ($\ref{eqn:garch}$) now follows a generalized error distribution with parameter $\theta$, i.e., $$\eta_{t} \stackrel{i i d}{\sim}GED(\theta).$$ Parameter estimates for monthly returns of the CRSP value weighted index from 1926 to 2003 are displayed in Table~\vref{tab:gjr-garch}. Since $\hat{\alpha}+\hat{\gamma} / 2+\hat{\beta}=0.958$ real return volatilities are close to nonstationary.
\begin{table}[!htbp] \centering 
  \caption{Parameter Estimates of the GJR-GARCH(1, 1)} 
  \label{tab:gjr-garch} 
  \begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 &  Estimate &  Rob. Std. Error &  Rob. t value & Pr(\textgreater \textbar t\textbar ) \\ 
\hline \\[-1.8ex] 
$\omega$ & $0.0001$ & $0.00004$ & $2.982$ & $0.003$ \\ 
$\alpha$ & $0.040$ & $0.025$ & $1.599$ & $0.110$ \\ 
$\beta$ & $0.861$ & $0.028$ & $30.881$ & $0.000$ \\ 
$\gamma$ & $0.114$ & $0.045$ & $2.562$ & $0.010$ \\ 
$\theta$ & $1.515$ & $0.089$ & $17.058$ & $0.000$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
 \begin{tablenotes}
 \small
\item Data is taken from Motohiro Yogo's website. Returns are the CRSP value weighted index log-returns from 1926 to 2003 minus the risk free rate.
\end{tablenotes}
\end{threeparttable}
\end{table}
Monte Carlo paths are simulated with $\omega = 0.000118$, $\gamma=0.0999$, $\theta=1.5$, $\alpha=0$ and letting $\beta$ increase to 0.95 such that the process approaches nonstationarity. The simulation outcome is displayed in Table~\vref{tab:mc_grj-garch}. It is observed that under realistic volatility modeling, the right-tailed Bonferroni Q-test tends to over-reject the true null.

\begin{table}[hbt]
\centering
\caption{Finite-sample rejection rates (common stochastic trend GJR-GARCH)}
\label{tab:mc_grj-garch}
\begin{threeparttable}
\begin{tabular}{rrrrrrrrrr}
  \hline
  & Obs & $c$ & $\rho$ & $\delta$ & $\alpha_{_{GARCH}}$ & $\beta_{_{GARCH}}$ & t-test &BQ& BQ$_{{2sided}}$ \\ 
  \hline
1 & 50 & -2 & 0.961 & -0.9500 & 0.0000 & 0.95 & 0.2836 & 0.1001 & 0.1033 \\ 
  2 & 50 & -2 & 0.961 & -0.9500 & 0.0000 & 0.90 & 0.2736 & 0.0946 & 0.0986 \\ 
  3 & 50 & -2 & 0.961 & -0.9500 & 0.0000 & 0.80 & 0.2635 & 0.0952 & 0.0993 \\ 
  4 & 100 & -2 & 0.980 & -0.9500 & 0.0000 & 0.95 & 0.3054 & 0.0757 & 0.0802 \\ 
  5 & 100 & -2 & 0.980 & -0.9500 & 0.0000 & 0.90 & 0.2811 & 0.0662 & 0.0727 \\ 
  6 & 100 & -2 & 0.980 & -0.9500 & 0.0000 & 0.80 & 0.2801 & 0.0685 & 0.0734 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed [BQ] and two-tailed  [BQ$_{{2sided}}$] Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with the variances of innovations sharing a common stochastic trend which is modeled as a univariate GJR-GARCH(1, 1) process. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\bibitem{} 
{Campbell, J. Y., Yogo, M. }
\textit{Efficient tests of stock return predictability.} Journal of Financial Economics 81, 27-60, 2006.
\bibitem{} 
{Elliott, G., Stock, J.H.} \textit{Inference in time series regression when the order of integration of a regressor is
unknown.} Econometric Theory 10, 672–700,  1994.
\bibitem{} 
Elliott, G., Rothenberg, T. J., \& Stock, J. H. (1996). Efficient Tests for an Autoregressive Unit Root. Econometrica, 64(4), 813–836.
\bibitem{} 
Jacquier, E., Polson, N.G., Rossi, P.E., 2004. Bayesian analysis of stochastic volatility
models with fat-tails and correlated errors. J. Econometrics 122, 185–212.
\bibitem{} 
Cavaliere, G., 2004. Unit root tests under time-varying variances. Econometric Rev.
23, 259–292.
\bibitem{} 
Phillips, P. C. B., 2014, On confdence Intervals for autoregressive roots and predictive regression. Econometrica, 82(3), 1177-1195.
\bibitem{} 
Bollerslev (1990): Modelling the coherence in short–run nominal exchange rates: a multivariate generalized ARCH model, Review of Economics and Statistics, 73, 498–505.
\bibitem{} 
Engle and Kroner (1995). Multivariate Simultaneous Generalized ARCH, Econometric Theory, 11, 122–150.
\bibitem{} 
Glosten, L. R., R. Jagannathan, and D. E. Runkle (1993). On the relation between the expected value and the volatility of the nominal excess return on stocks. The Journal of Finance 48, 1779-1801.
\end{thebibliography}
